Out-of-Sample Comparisons of Overfit Models

### 2014-02-25 paper.tex
Tweak footnote source to make line-wrap work better

\section{Introduction}\label{sec:introduction}
Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use OOS instead of in-sample
comparisons: the DMW OOS test\footnote{In this paper, we will
  refer to the basic OOS $t$-test studied by \citet{DiM:95} and
  \citet{Wes:96} as the DMW test.} allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo
that standard full-sample test statistics can not test hypotheses
about this performance.

@@

Although OOS comparisons have been popular in Macroeconomics and
Finance since \citepos{MeR:83} seminal study of exchange rate models,
it has been unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using OOS comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the $F$-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular OOS test statistics under conditions
that would justify these full-sample tests.  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons \citep[see][for a
review of this literature]{Wes:06}.\footnote{Like us, \citet{Ana:07}
  allows the number of regressors to increase with $T$.  But in that
  paper, the number of regressors increases slowly enough that the OLS
  coefficients are consistent and asymptotically normal.} \citet{GiW:06} and
\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
derive an OOS test for the null hypothesis that the difference
between two models' OOS forecasting performance is unpredictable, a
martingale difference sequence; \citet{GiR:09} test whether the OOS
forecasting performance of a model suffers from a breakdown relative
to its in-sample performance; and \citet{GiR:10} test whether the
forecasting performance is stable. However, those papers focus on a
particular OOS estimation strategy and do not address why OOS
comparisons might be useful as a general strategy.

@@

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic
conclusions should be true for other models as well.  Under this
asymptotic theory, where the number of regressors $k$ increases with $T$
so that $\lim k/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the on the data available in period
$T$.\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.}  Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudo-true
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the DGP that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do OOS comparisons.}
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99} and
\citealp{StW:03} among others), but this breakdown can be caused by overfit as
well.

@@

Popular in-sample tests and model selection criteria, like the Wald
test, AIC, and BIC, do not help forecasters in this setting. We show
that these statistics can no pick out the more accurate model. For
many DGPs they will choose a larger alternative model over a small
benchmark model with probability approaching one, regardless of which
model is more accurate.\footnote{Our result holds for a broad class of
  full-sample statistics, but there may be other potential statistics
  that mimic the OOS test and remain valid. Exploring such
  statistics is left for future research.}
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
  of naive in-sample loss comparisons.}
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.\footnote{Our theoretical results apply
  directly to \citepos{Mcc:07} OOS $t$-test, since it simply
  proposes more liberal critical values for the same test statistic
  that we study.  Since \citet{ClW:06,ClW:07} use a finite length
  estimation window, our asymptotics are incompatible with theirs and
  prevent us from studying their test directly, as well as
  \citepos{GiW:06} and other tests based on \citepos{GiW:06}
  asymptotics.  But \clws\ test can be viewed as a stochastic
  adjustment to the critical values of the usual OOS $t$ test, so
  our conclusions should apply informally as well.  Specifically, we
  show that the DMW test rejects with probability equal to nominal
  size when the estimated benchmark model is expected to be more
  accurate, so more liberal critical values result in overrejection.}
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

@@

\section{Setup and Assumptions}\label{sec:assumptions}
The first part of this section will describe the environment in detail
and set up our models and notation. The second part will list the
assumptions underlying our theoretical results.

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\begin{equation}
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\end{equation}
$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
The coefficients $\theta_1$ and $\theta_2$ minimize the population
Mean Square Error, so
\begin{equation}
  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
\end{equation}
making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
serial correlation so both of the linear models may be misspecified.
Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
set available in period $t$,
with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$. At least one of the models is
overfit, which we represent asymptotically by letting $K_2$ grow with
$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
$T$ as well. Since the models change with $T$, a
stochastic array underlies all of our asymptotic theory, but we
suppress that notation to simplify the presentation.

In the settings we are interested in, a forecaster observes the data
$(y_t,x_t)$ for periods 1 through $T$ and divides the observations
into an estimation sample of the first $R$ observations and a test
sample of the remaining $P$ observations. The forecaster then compares
the models' performance over the test sample, which entails
constructing two sequences of forecasts, (using a fixed-window
estimation strategy)
\begin{equation}
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
\ t = R+1,\dots,T-h,
\end{equation}
where
\begin{equation}
  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{It
    may not be clear why we are using a $t$ index in $\bh{it}$,
    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
    But $\bh{it}$ will be defined for $t > T-\h$
    soon and will not equal $\bh{iR}$ for those values of $t$.}
\end{equation}

The models are then compared by their forecast errors over the test
sample.  There are many statistics that have been considered in the
literature, but we focus on perhaps the most natural, the DMW \oost\
test \citep{DiM:95,Wes:96}.\footnote{The core insights of our paper
  apply to other OOS statistics as well.} This statistic is based on
the difference in the models' loss over the test sample, $\oosA$,
defined as
\begin{equation}
  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
\end{equation}
where
\begin{equation}\label{eq:16}
  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
\end{equation}
and $L$ is a known loss function. The \oost\ test is defined as
$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
Autocorrelation-Consistent, or HAC, estimator.)

@@

Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
converge in probability to the difference in the expected loss
associated with the pseudo-true models,\footnote{Under standard
  stationarity, moment, and weak-dependence conditions.}

i.e. the LHS of~\eqref{eq:21}.
\begin{equation}\label{eq:22}
  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
\end{equation}
But if $K_2$ increases with $T$ these quantities can have different
limits. For a simple example, assume squared-error loss, let $x_{1,t}
= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
\Sigma)$.  Then
\begin{align*}
  \E_T \oosB - & \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 - \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) -
  \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
  &= (\bh{2,t} - \theta_2)' \Sigma_x (\bh{2,t} - \theta_2) + o_p(1).
\end{align*}
This last term has expectation $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
would converge to zero if $K_2$ were fixed, but does not when $\lim
K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
statistic can estimate $\E_T \oosB$ under our increasing $K$
asymptotics and does not estimate the expected loss associated with
the pseudo-true coefficients.

@@

Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
\citepos{Wes:96} assumptions, except with regard to model complexity
and the size of the test sample.  West assumes that $K_1$ and $K_2$
are both finite, while we let them grow rapidly with $T$
(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
in $[0,\infty]$, while we require $P^2/R \to 0$
(Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
  second OOS period, so there is no analogue in his paper to our
  restriction on $Q$.}  Obviously, these differences are
related---allowing for complex models requires tighter constraints on
the size of the test sample.  West allows more general estimation
methods, while we restrict attention to OLS; the advantage of using
OLS is that we can derive the inequality,
\begin{equation*}
  \| x_{it}'\bh{i,T+1} - x_{it}'\bh{iR} \|_2 \leq O(P/T)^{1/2}.
\end{equation*}
Our main results will hold for other models and estimation windows as
long as a similar inequality exists, but proving such inequalities is
left for future research.

@@

\subsection{Failure of In-Sample Tests}\label{sec:insample}
This subsection establishes that in-sample tests like the $F$-test can
overreject when the benchmark is more accurate than the alternative.
The issue explored here is different than that of \citet{Cal:11c} and
\citet{Ana:12}; in those papers, the authors demonstrate that full
sample Wald and $F$-tests can be invalid under increasing-$k$
asymptotics,\footnote{\citet{Ana:12} shows that the Wald test is
  invalid in general and gives an adjustment that corrects the
  critical values; he also shows that the $F$-test is asymptotically
  valid under certain conditions on the distribution of the
  regressors.  \citet{Cal:11c} shows that the $F$-test is
  asymptotically invalid without Anatolyev's constraint, and provides
  a correction that gives valid tests.  Both papers only consider
  independent observations.} e.g. they can overreject when testing the
null hypotheses that a set of the coefficients is zero.  This paper,
though, looks at the behavior when the coefficients are non-zero but
the estimated restricted model is more accurate.  In this setting,
these tests reject the benchmark too often---more than their nominal
size---and for most coefficient values will reject almost surely in
the limit.  We also look at some common model selection statistics and
find the same conclusion---they choose the larger model with high
probability regardless of which model will forecast better.  To
simplify the presentation, we'll only present results for nested
models.

@@

Theorem~\ref{res:ftest} covers a broad class of test statistics and
allows the in-sample test to be valid or invalid in finite samples or
asymptotically.  It implies that a large class of in-sample tests will
reject if $\theta$ is nonzero, whether or not the alternative model is
more accurate.  As an example, consider the $F$-test of the null
hypothesis $A \theta =0$ with deterministic regressors and
i.i.d. Normal errors where $\rank A = J$ and $\lim J/T > 0$.  Simple
algebra reveals that the test rejects if $\hat{\theta}_T' V_T
\hat{\theta}_T \geq 1$ with
\begin{equation*}
  V_T = (T/ J \hat{\xi}^{2}) A' (A (T^{-1}X_T'X_T)^{-1} A')^{-1} A;
\end{equation*}
$\xi^2$ is the variance of the model's innovations and $\hat{\xi}^2$ is
the usual estimator based on the squared residuals.  Note that $\rank
V_T = \rank A$ as long as $X_T'X_T$ is full rank.  Under the null $A
\theta = 0$,
\begin{equation*}
  \hat{\theta}_T' V_T
  \hat{\theta}_T =^d   (\xi^2/ J \hat{\xi}^2) \chi_J^2 =^d 1 + J^{-1/2} Z
  + o_p(T^{-1/2}),
\end{equation*}
where $\chi_J^2$ is an independent $\chi^2$ random variable with $J$
degrees of freedom and $Z \sim N(0,1)$.  Consequently, the $F$-test
accepts whenever $\hat{\theta}_T$ is in a neighborhood of the cylinder
defined by $\hat{\theta}_T' V_T \hat{\theta}_T = 1$ and rejects for
$\hat{\theta}_T$ outside the neighborhood.\footnote{If $V_T$ is full
  rank, this equation defines an ellipsoid in $\mathbb{R}^K$;
  otherwise the equation defines an ellipsoid in a subspace of
  $\mathbb{R}^K$.}  The neighborhood shrinks as $T \to \infty$, so the
$F$-test satisfies the conditions of Theorem~\ref{res:ftest} with
$V_T$ as given above and $c = 1 + \delta$ for any $\delta > 0$.
Notice that $c$ does not depend on the nominal size of the test and
that the exact finite sample distribution of the $F$-test is known in
this example, so the test is valid by conventional measures but the
conclusions of Theorem~\ref{res:ftest} still hold.

@@

Table~\ref{tab:gwinsample} gives the results of the full sample
regression for Equation~\eqref{eq:2}, using Newey-West standard errors
with two lags \citep{NeW:87}.\footnote{We compare the test statistic
  to critical values from the $F$-distribution.}  The $p$-value is
very small (less than 0.01), indicating that the coefficients are
nonzero in population and at least one of these predictors is
correlated with the equity premium.  As we argue earlier, this result
does not imply that the model will forecast well, which we look at
next.

>>>>

\section{Introduction}\label{sec:introduction}
Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use OOS instead of in-sample
comparisons: the DMW OOS test%
\footnote{In this paper, we will refer to the basic OOS $t$-test
  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo
that standard full-sample test statistics can not test hypotheses
about this performance.

@@

Although OOS comparisons have been popular in Macroeconomics and
Finance since \citepos{MeR:83} seminal study of exchange rate models,
it has been unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using OOS comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the $F$-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular OOS test statistics under conditions
that would justify these full-sample tests.  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons \citep[see][for a
review of this literature]{Wes:06}.%
\footnote{Like us, \citet{Ana:07} allows the number of regressors to
  increase with $T$.  But in that paper, the number of regressors
  increases slowly enough that the OLS coefficients are consistent and
  asymptotically normal.} %
\citet{GiW:06} and
\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
derive an OOS test for the null hypothesis that the difference
between two models' OOS forecasting performance is unpredictable, a
martingale difference sequence; \citet{GiR:09} test whether the OOS
forecasting performance of a model suffers from a breakdown relative
to its in-sample performance; and \citet{GiR:10} test whether the
forecasting performance is stable. However, those papers focus on a
particular OOS estimation strategy and do not address why OOS
comparisons might be useful as a general strategy.

@@

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic
conclusions should be true for other models as well.  Under this
asymptotic theory, where the number of regressors $k$ increases with $T$
so that $\lim k/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the on the data available in period
$T$.%
\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.} %
Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudo-true
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.%
\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the DGP that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do OOS comparisons.} %
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99} and
\citealp{StW:03} among others), but this breakdown can be caused by overfit as
well.

@@

Popular in-sample tests and model selection criteria, like the Wald
test, AIC, and BIC, do not help forecasters in this setting. We show
that these statistics can no pick out the more accurate model. For
many DGPs they will choose a larger alternative model over a small
benchmark model with probability approaching one, regardless of which
model is more accurate.%
\footnote{Our result holds for a broad class of
  full-sample statistics, but there may be other potential statistics
  that mimic the OOS test and remain valid. Exploring such
  statistics is left for future research.} %
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.%
\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
  of naive in-sample loss comparisons.} %
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.%
\footnote{Our theoretical results apply
  directly to \citepos{Mcc:07} OOS $t$-test, since it simply
  proposes more liberal critical values for the same test statistic
  that we study.  Since \citet{ClW:06,ClW:07} use a finite length
  estimation window, our asymptotics are incompatible with theirs and
  prevent us from studying their test directly, as well as
  \citepos{GiW:06} and other tests based on \citepos{GiW:06}
  asymptotics.  But \clws\ test can be viewed as a stochastic
  adjustment to the critical values of the usual OOS $t$ test, so
  our conclusions should apply informally as well.  Specifically, we
  show that the DMW test rejects with probability equal to nominal
  size when the estimated benchmark model is expected to be more
  accurate, so more liberal critical values result in overrejection.} %
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

@@

\section{Setup and assumptions}\label{sec:assumptions}

The first part of this section will describe the environment in detail
and set up our models and notation. The second part will list the
assumptions underlying our theoretical results.

\subsection{Notation and forecasting environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\begin{equation}
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\end{equation}
$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
The coefficients $\theta_1$ and $\theta_2$ minimize the population
Mean Square Error, so
\begin{equation}
  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
\end{equation}
making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
serial correlation so both of the linear models may be misspecified.
Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
set available in period $t$,
with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$. At least one of the models is
overfit, which we represent asymptotically by letting $K_2$ grow with
$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
$T$ as well. Since the models change with $T$, a
stochastic array underlies all of our asymptotic theory, but we
suppress that notation to simplify the presentation.

In the settings we are interested in, a forecaster observes the data
$(y_t,x_t)$ for periods 1 through $T$ and divides the observations
into an estimation sample of the first $R$ observations and a test
sample of the remaining $P$ observations. The forecaster then compares
the models' performance over the test sample, which entails
constructing two sequences of forecasts, (using a fixed-window
estimation strategy)
\begin{equation}
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
\ t = R+1,\dots,T-h,
\end{equation}
where
\begin{equation}
  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
\footnote{It may not be clear why we are using a $t$ index in $\bh{it}$,
    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
    But $\bh{it}$ will be defined for $t > T-\h$
    soon and will not equal $\bh{iR}$ for those values of $t$.} %
\end{equation}

The models are then compared by their forecast errors over the test
sample.  There are many statistics that have been considered in the
literature, but we focus on perhaps the most natural, the DMW \oost\
test \citep{DiM:95,Wes:96}.%
\footnote{The core insights of our paper apply to other OOS statistics
  as well.} %
This statistic is based on
the difference in the models' loss over the test sample, $\oosA$,
defined as
\begin{equation}
  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
\end{equation}
where
\begin{equation}\label{eq:16}
  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
\end{equation}
and $L$ is a known loss function. The \oost\ test is defined as
$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
Autocorrelation-Consistent, or HAC, estimator.)

@@

Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
converge in probability to the difference in the expected loss
associated with the pseudo-true models,%
\footnote{Under standard stationarity, moment, and weak-dependence
  conditions.} %
i.e. the LHS of~\eqref{eq:21}.
\begin{equation}\label{eq:22}
  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
\end{equation}
But if $K_2$ increases with $T$ these quantities can have different
limits. For a simple example, assume squared-error loss, let $x_{1,t}
= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
\Sigma)$.  Then
\begin{align*}
  \E_T \oosB - & \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 - \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) -
  \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
  &= (\bh{2,t} - \theta_2)' \Sigma_x (\bh{2,t} - \theta_2) + o_p(1).
\end{align*}
This last term has expectation $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
would converge to zero if $K_2$ were fixed, but does not when $\lim
K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
statistic can estimate $\E_T \oosB$ under our increasing $K$
asymptotics and does not estimate the expected loss associated with
the pseudo-true coefficients.

@@

Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
\citepos{Wes:96} assumptions, except with regard to model complexity
and the size of the test sample.  West assumes that $K_1$ and $K_2$
are both finite, while we let them grow rapidly with $T$
(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
in $[0,\infty]$, while we require $P^2/R \to 0$
(Assumption~\ref{asmp-4}).%
\footnote{\citet{Wes:96} does not have a
  second OOS period, so there is no analogue in his paper to our
  restriction on $Q$.} %
Obviously, these differences are
related---allowing for complex models requires tighter constraints on
the size of the test sample.  West allows more general estimation
methods, while we restrict attention to OLS; the advantage of using
OLS is that we can derive the inequality,
\begin{equation*}
  \| x_{it}'\bh{i,T+1} - x_{it}'\bh{iR} \|_2 \leq O(P/T)^{1/2}.
\end{equation*}
Our main results will hold for other models and estimation windows as
long as a similar inequality exists, but proving such inequalities is
left for future research.

@@

\subsection{Failure of in-sample forecast evaluation}\label{sec:insample}
This subsection establishes that in-sample tests like the $F$-test can
overreject when the benchmark is more accurate than the alternative.
The issue explored here is different than that of \citet{Cal:11c} and
\citet{Ana:12}; in those papers, the authors demonstrate that full
sample Wald and $F$-tests can be invalid under increasing-$k$
asymptotics,%
\footnote{\citet{Ana:12} shows that the Wald test is
  invalid in general and gives an adjustment that corrects the
  critical values; he also shows that the $F$-test is asymptotically
  valid under certain conditions on the distribution of the
  regressors.  \citet{Cal:11c} shows that the $F$-test is
  asymptotically invalid without Anatolyev's constraint, and provides
  a correction that gives valid tests.  Both papers only consider
  independent observations.} %
e.g. they can overreject when testing the
null hypotheses that a set of the coefficients is zero.  This paper,
though, looks at the behavior when the coefficients are non-zero but
the estimated restricted model is more accurate.  In this setting,
these tests reject the benchmark too often---more than their nominal
size---and for most coefficient values will reject almost surely in
the limit.  We also look at some common model selection statistics and
find the same conclusion---they choose the larger model with high
probability regardless of which model will forecast better.  To
simplify the presentation, we'll only present results for nested
models.

@@

Theorem~\ref{res:ftest} covers a broad class of test statistics and
allows the in-sample test to be valid or invalid in finite samples or
asymptotically.  It implies that a large class of in-sample tests will
reject if $\theta$ is nonzero, whether or not the alternative model is
more accurate.  As an example, consider the $F$-test of the null
hypothesis $A \theta =0$ with deterministic regressors and
i.i.d. Normal errors where $\rank A = J$ and $\lim J/T > 0$.  Simple
algebra reveals that the test rejects if $\hat{\theta}_T' V_T
\hat{\theta}_T \geq 1$ with
\begin{equation*}
  V_T = (T/ J \hat{\xi}^{2}) A' (A (T^{-1}X_T'X_T)^{-1} A')^{-1} A;
\end{equation*}
$\xi^2$ is the variance of the model's innovations and $\hat{\xi}^2$ is
the usual estimator based on the squared residuals.  Note that $\rank
V_T = \rank A$ as long as $X_T'X_T$ is full rank.  Under the null $A
\theta = 0$,
\begin{equation*}
  \hat{\theta}_T' V_T
  \hat{\theta}_T =^d   (\xi^2/ J \hat{\xi}^2) \chi_J^2 =^d 1 + J^{-1/2} Z
  + o_p(T^{-1/2}),
\end{equation*}
where $\chi_J^2$ is an independent $\chi^2$ random variable with $J$
degrees of freedom and $Z \sim N(0,1)$.  Consequently, the $F$-test
accepts whenever $\hat{\theta}_T$ is in a neighborhood of the cylinder
defined by $\hat{\theta}_T' V_T \hat{\theta}_T = 1$ and rejects for
$\hat{\theta}_T$ outside the neighborhood.%
\footnote{If $V_T$ is full
  rank, this equation defines an ellipsoid in $\mathbb{R}^K$;
  otherwise the equation defines an ellipsoid in a subspace of
  $\mathbb{R}^K$.} %
The neighborhood shrinks as $T \to \infty$, so the
$F$-test satisfies the conditions of Theorem~\ref{res:ftest} with
$V_T$ as given above and $c = 1 + \delta$ for any $\delta > 0$.
Notice that $c$ does not depend on the nominal size of the test and
that the exact finite sample distribution of the $F$-test is known in
this example, so the test is valid by conventional measures but the
conclusions of Theorem~\ref{res:ftest} still hold.

@@

Table~\ref{tab:gwinsample} gives the results of the full sample
regression for Equation~\eqref{eq:2}, using Newey-West standard errors
with two lags \citep{NeW:87}.%
\footnote{We compare the test statistic
  to critical values from the $F$-distribution.} %
The $p$-value is
very small (less than 0.01), indicating that the coefficients are
nonzero in population and at least one of these predictors is
correlated with the equity premium.  As we argue earlier, this result
does not imply that the model will forecast well, which we look at
next.
